\textsf{Are large language models superhuman chemists?}

### 2024-03-27 src/tex/appendix.tex
add matbench reference

>>>>

\subsection{Leaderboard}
Our leaderboard is based on the tool chain developed for matbench.\autocite{Dunn_2020} Briefly, the \chembench pipeline produces standardized files in \texttt{json} format that contributors can add via pull requests to the \chembench repository.
The Markdown tables and plots are then automatically generated and updated on the \chembench website.

### 2024-03-27 src/tex/ms.tex
add note about leaderboard
add matbench reference

\clearpage
\begin{refsection}
\section{Introduction}
\Glspl{llm} are \gls{ml} models trained on massive amounts of text to complete sentences. 
Aggressive scaling of these models has led to a rapid increase in their capabilities,\autocite{brown2020language,zhong2024benchmarking} with the leading models now being able to pass in some evaluations the United States Medical Licensing Examination\cite{kung2023performance} or identify and autonomously buy chemicals when augmented with external tools such as web search and synthesis planners.\autocite{openai2024gpt4}
While some see \enquote{sparks of \gls{agi}} in them,\autocite{bubeck2023sparks} others consider them as \enquote{stochastic parrots}---i.e., systems that only regurgitate what they have been trained on.\autocite{bender2021dangers}
In any case, the promise of so-called foundation models (the leading ones being called frontier models) is that they show the ability to solve a wide variety of tasks they have not been explicitly trained on.\autocite{bommasani2021opportunities, anderljung2023frontier}
This led to tremendous economic interest and investment in such generative models, with an expected market of more than \$1.3 trillion (almost \$30 billion for drug discovery applications) by 2032.\autocite{bloomberg}

@@

It is important to note that the model performance for some topics, however, is underestimated in the current evaluation. This is because models that are provided via \glspl{api} typically have safety mechanisms that prevent them from providing answers that the provider deems unsafe.
For instance, models might refuse to provide answers about cyanides. To overcome this, direct access to the model weights would be required, and we strive to collaborate with the developers of frontier models to overcome this limitation in the future.

>>>>

\clearpage
\begin{refsection}
\section{Introduction}
\Glspl{llm} are \gls{ml} models trained on massive amounts of text to complete sentences. 
Aggressive scaling of these models has led to a rapid increase in their capabilities,\autocite{brown2020language,zhong2024benchmarking} with the leading models now being able to pass in some evaluations the United States Medical Licensing Examination\autocite{kung2023performance} or identify and autonomously buy chemicals when augmented with external tools such as web search and synthesis planners.\autocite{openai2024gpt4}
While some see \enquote{sparks of \gls{agi}} in them,\autocite{bubeck2023sparks} others consider them as \enquote{stochastic parrots}---i.e., systems that only regurgitate what they have been trained on.\autocite{bender2021dangers}
In any case, the promise of so-called foundation models (the leading ones being called frontier models) is that they show the ability to solve a wide variety of tasks they have not been explicitly trained on.\autocite{bommasani2021opportunities, anderljung2023frontier}
This led to tremendous economic interest and investment in such generative models, with an expected market of more than \$1.3 trillion (almost \$30 billion for drug discovery applications) by 2032.\autocite{bloomberg}

@@

It is important to note that the model performance for some topics, however, is underestimated in the current evaluation. This is because models that are provided via \glspl{api} typically have safety mechanisms that prevent them from providing answers that the provider deems unsafe.
For instance, models might refuse to provide answers about cyanides. To overcome this, direct access to the model weights would be required, and we strive to collaborate with the developers of frontier models to overcome this limitation in the future.
This is facilitated with the tooling \chembench provides, thanks to which new models can be automatically added by contributors in an open science fashion.
